07-logistic_regression

### 2019-02-26 journals/07-logistic_regression/07-logistic_regression.Rmd
worked more on logistic regression

```{r}
# Fit or load the logistic regression model with only main effects
if(!file.exists("../../data/logistic_mains.rds")) {

@@

  # Save the model
  saveRDS(logistic_mains, "../../data/logistic_mains.rds")

@@

  # Load the model
  logistic_mains <- readRDS("../../data/logistic_mains.rds")

@@

```{r}
# Fit or load the logistic regression model with all two way interactions
if(!file.exists("../../data/logistic_inters2.rds")) {

@@

  # Save the model
  saveRDS(logistic_inters2, "../../data/logistic_inters2.rds")

@@

   # Load the model
  logistic_inters2 <- readRDS("../../data/logistic_inters2.rds")

@@

```{r eval = FALSE}
# Fit or load the logistic regression model with all two and three way interactions
if(!file.exists("../../data/logistic_inters3.rds")) {

@@

  # Save the model
  saveRDS(logistic_inters3, "../../data/logistic_inters3.rds")

@@

  # Load the model
  logistic_inters3 <- readRDS("../../data/logistic_inters3.rds")

@@

```{r eval = FALSE}
# Summary of the model
summary(logistic_inters3)
```

@@

```{r eval = FALSE}
logistic_mains_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
                            model = logistic_mains$finalModel)

logistic_mains_explain <- explain(x = hamby224_test %>% 
                                    select(rf_features) %>% 
                                    na.omit(), 
                                  explainer = logistic_mains_lime, 
                                  n_labels = 1,
                                  n_features = 3)

plot_features(logistic_mains_explain[1:12,])
```

@@

```{r eval = FALSE}
logistic_inters2_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
                              model = logistic_inters2)

logistic_inters2_explain <- explain(x = hamby224_test %>% 
                                      select(rf_features) %>% 
                                      na.omit(), 
                                    explainer = logistic_inters2_lime, 
                                    n_labels = 1,
                                    n_features = 3)

plot_features(logistic_inters2_explain[1:12,])
```

@@

```{r eval = FALSE}
logistic_inters3_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
                              model = logistic_inters3)

logistic_inters3_explain <- explain(x = hamby224_test %>% 
                                      select(rf_features) %>% 
                                      na.omit(), 
                                    explainer = logistic_inters3_lime, 
                                    n_labels = 1,
                                    n_features = 3)

plot_features(logistic_inters3_explain[1:12,])
```

>>>>

```{r}
# Fit or load the logistic regression model with only main effects
if(!file.exists("./data/logistic_mains.rds")) {

@@

  # Save the model
  saveRDS(logistic_mains, "./data/logistic_mains.rds")

@@

  # Load the model
  logistic_mains <- readRDS("./data/logistic_mains.rds")

@@

```{r}
# Fit or load the logistic regression model with all two way interactions
if(!file.exists("./data/logistic_inters2.rds")) {

@@

  # Save the model
  saveRDS(logistic_inters2, "./data/logistic_inters2.rds")

@@

   # Load the model
  logistic_inters2 <- readRDS("./data/logistic_inters2.rds")

@@

```{r}
# Fit or load the logistic regression model with all two and three way interactions
if(!file.exists("./data/logistic_inters3.rds")) {

@@

  # Save the model
  saveRDS(logistic_inters3, "./data/logistic_inters3.rds")

@@

  # Load the model
  logistic_inters3 <- readRDS("./data/logistic_inters3.rds")

@@

The output from this model is now shown.

@@

The functions `lime` and `explain` from the lime package are applied below to the logisitc regression model with only main effects.

```{r}
# Create or load the lime and explain objects for the main effects logisitic regression model
if(!file.exists("./data/lime_explain_mains.rds")) {

  # Apply lime
  lime_mains <- lime(x = hamby173and252_train %>% select(rf_features), 
                     model = logistic_mains)

  # Apply explain
  explain_mains <- explain(x = hamby224_test %>%
                             select(rf_features) %>% 
                             na.omit(), 
                           explainer = logistic_mains_lime, 
                           n_labels = 1,
                           n_features = 3)

  # Join the lime and explain objects in a list
  lime_explain_mains <- list(lime = lime_mains, explain = explain_mains)

  # Save the lime and explain objects
  saveRDS(lime_explain_mains, "./data/lime_explain_mains.rds")

} else {

  # Load the lime and explain objects
  lime_explain_mains <- readRDS("./data/lime_explain_mains.rds")

```{r}
plot_features(lime_explain_mains$explain[1:12,])
```

@@

```{r}
# Create or load the lime and explain objects for the two way interaction logisitic regression model
if(!file.exists("./data/lime_explain_inters2.rds")) {

  # Apply lime
  lime_inters2 <- lime(x = hamby173and252_train %>% select(rf_features), 
                       model = logistic_inters2)

  # Apply explain
  explain_inters2 <- explain(x = hamby224_test %>%
                               select(rf_features) %>% 
                               na.omit(), 
                             explainer = logistic_inters2_lime, 
                             n_labels = 1,
                             n_features = 3)

  # Join the lime and explain objects in a list
  lime_explain_inters2 <- list(lime = lime_inters2, explain = explain_inters2)

  # Save the lime and explain objects
  saveRDS(lime_explain_inters2, "./data/lime_explain_inters2.rds")

} else {

  # Load the lime and explain objects
  lime_explain_inters2 <- readRDS("./data/lime_explain_inters2.rds")

```{r}
plot_features(lime_explain_inters2$explain[1:12,])
```

@@

```{r}
# Create or load the lime and explain objects for the three way interaction logisitic regression model
if(!file.exists("./data/lime_explain_inters3.rds")) {

  # Apply lime
  lime_inters3 <- lime(x = hamby173and252_train %>% select(rf_features), 
                       model = logistic_inters3)

  # Apply explain
  explain_inters3 <- explain(x = hamby224_test %>%
                               select(rf_features) %>% 
                               na.omit(), 
                             explainer = logistic_inters3_lime, 
                             n_labels = 1,
                             n_features = 3)

  # Join the lime and explain objects in a list
  lime_explain_inters3 <- list(lime = lime_inters3, explain = explain_inters3)

  # Save the lime and explain objects
  saveRDS(lime_explain_inters3, "./data/lime_explain_inters3.rds")

} else {

  # Load the lime and explain objects
  lime_explain_inters3 <- readRDS("./data/lime_explain_inters3.rds")

```{r}
plot_features(lime_explain_inters3$explain[1:12,])
```
